Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-11 papers/marlowe2019/paper.tex
Fixes, comments.

\noindent
Marlowe contract execution on the blockchain consists of a chain of transactions
where, at each stage, the remaining contract and its state are passed through the \emph{Data script},
and actions and inputs (i.e. \emph{choices} and \emph{money deposits}) are passed to the %SJT: is this irght?
\emph{Redeemer}.
Each step in contract execution is a transaction that spends a Marlowe contract transaction output
by providing a valid input as \emph{Redeemer}, and produces a transaction output
with a the remaining Marlowe contract and the updated state.

@@

\begin{itemize}%SJT: DoS usually means denial of service?
    \item It reduces the danger of Denegation of Service (DoS) attacks: because the number of valid inputs is limited, an attacker participant cannot arbitrarily block the contract by issuing an unbounded amount of useless \texttt{Transaction}s.
    \item The number of transactions bounds the length of traces that symbolic execution (see Section~\ref{sec:static}) needs to explore (more on this below).%SJT: is this really below? Or above?
\end{itemize}

@@

Contracts written in the Marlowe editor are parsed in real-time and if there are no errors (and no holes) then the contract is analysed to discover which actions a user could take to progress the contract. These actions are displayed in the ``Input Composer'' above the editor. Consider the following example contract:
\begin{verbatim}
    When [Case (Deposit (AccountId 0 "investor") 
               "guarantor" (Constant 1000)) Close] 10 Close
\end{verbatim}
In this case, the only action a user can take to progress the contract is to accept a deposit of 1000 ADA
%SJT: we need to sort out the Ada/Lovelance mismatch.
from the guarantor to the investor's account. Because of this, the playground can display this action in the input composer.

>>>>

\noindent
Marlowe contract execution on the blockchain consists of a chain of transactions
where, at each stage, the remaining contract and its state are passed through the \emph{Data script},
and actions/inputs (i.e. \emph{choices} and \emph{money deposits}) are passed via the 
%SJT: is this right?
%AN: yes. [Input] is precisely the redeemer script. We could say that Value and SlotInterval are parts of PendingTx,
% but I think it's not that important here.
\emph{Redeemer}.
Each step in contract execution is a transaction that spends a Marlowe contract transaction output
by providing a valid input as \emph{Redeemer}, and produces a transaction output
with a the remaining Marlowe contract and the updated state.

@@

\begin{itemize}
    \item It reduces the danger of Denial of Service (DoS) attacks: because the number of valid inputs is limited, an attacker participant cannot arbitrarily block the contract by issuing an unbounded amount of useless \texttt{Transaction}s.
    \item The number of transactions bounds the length of traces that symbolic execution (see Section~\ref{sec:static}) needs to explore (more on this below).%SJT: is this really below? Or above?
\end{itemize}

@@

Contracts written in the Marlowe editor are parsed in real-time and if there are no errors (and no holes) then the contract is analysed to discover which actions a user could take to progress the contract. These actions are displayed in the ``Input Composer'' above the editor. Consider the following example contract:
\begin{verbatim}
    When [Case (Deposit (AccountId 0 "investor") 
               "guarantor" (Constant 1000_000000)) Close] 10 Close
\end{verbatim}
In this case, the only action a user can take to progress the contract is to accept a deposit of 1000 ADA
from the guarantor to the investor's account. Because of this, the playground can display this action in the input composer.
